### 2020-03-29 temp/Paper_EV/Paper_EV.tex
backup update 28_03

% Add List of Tables
\renewcommand{\cfttabfont}{Table }				% Add "Figure" to the LOF
\renewcommand\cfttabaftersnum{:} 				% Put ":" after the figure num 
\setlength{\cfttabindent}{0pt}					% Remove left indent
\setlength\cftbeforetabskip{-0.2cm}				% Space between tables
\addtocontents{lot}{\vspace*{10pt}}			    % Set distance between LOT title and list
\listoftables{}

% Manually add Chapter names to the header (per default not included by Latex)
\thispagestyle{fancy_beginning}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\chaptermark{List of Tables}

%Insert empty page after the list of tables 
\newpage\null\thispagestyle{empty}\newpage

@@

% Add Table of Symbols
%\chapter*{Table of Symbols} \label{sec:symbols}
\mbox{}
\nomwithdim{B}{\( \bm{F} \)}{Force}{L}{$N$}
\nomwithdim{B}{\( g \)}{Gravitational acceleration}{}{$m/s^2$}
\nomwithdim{G}{\( \alpha \)}{Angle of attack}{}{$rad$}
\nomwithdim{G}{\( \zeta \)}{Damping of a linear second order system}{}{--}
\nomwithdim{S}{\( m \)}{Variable related to pitch moment}{}{}
\nomwithdim{S}{\( W \)}{Wind}{}{}
\renewcommand{\nomname}{Table of Symbols}
\printnomenclature[6em]

% Manually add Chapter names to the header (per default not included by Latex)
\thispagestyle{fancy_beginning}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\chaptermark{Table of Symbols}

@@

In this subsection, the \acrfull{NDI} method is explained. The \acrshort{NDI} approach is based on feedback linearization and is also called \textit{Input-Output Linearization}. Often, such type of controllers is involved in tracking control tasks, where the objective is to track some desired trajectory \cite{Slotine}. To derive it, consider the following nonlinear system
\begin{subequations}
	\begin{align}
		&\bm{\dot{x}} = \bm{f}(\bm{x}) + \bm{G}(\bm{x})\bm{u} \label{eq:nonlin_sys1} \\
		&\bm{y} = \bm{h}(\bm{x}) \label{eq:nonlin_sys2}
	\end{align}
	\label{eq:nonlin_sys}
\end{subequations}
\hspace{-5pt}where $\bm{x} \in \mathbb{R}^{n \times 1}$ is the state vector, $\bm{u} \in \mathbb{R}^{m \times 1}$ the input vector, $\bm{y} \in \mathbb{R}^{m \times 1}$ the output vector, $\bm{f}(\bm{x}) \in \mathbb{R}^{n \times 1}$ and $\bm{h}(\bm{x}) \in \mathbb{R}^{m \times 1}$ nonlinear vector fields and $\bm{G} \in \mathbb{R}^{m \times n}$ an input matrix. Note that the system presented in Equations (\ref{eq:nonlin_sys}) is affine in the input, which is not allways fulfilled. Using a state transformation $\bm{z} = \bm{\phi}(\bm{x})$, the affine system from Equation \ref{eq:nonlin_sys1} can be transformed into a \textit{normal} (\textit{canonical}) representation.

@@

In the example provided above the input-output relationsip was found after the first differentiation of the output $\bm{y}$. But if after the first differentiation the term $L_{\bm{G}}\bm{h}(\bm{x})$ is zero, output $\bm{y}$ has to be differentiated until the Lie derivative with respect to $\bm{G}$ is nonzero. The $i$-th derivative of the output is then
\begin{equation}
	\begin{split}
		\frac{\partial^i\bm{y}}{\partial t} = \frac{\partial^i\bm{h}(\bm{x})}{\partial t} = L_{\bm{f}}^i \bm{h}(\bm{x}) + L_{\bm{G}} L_{\bm{f}}^{i-1} \bm{h}(\bm{x}) \bm{u}
		\label{eq:dy_i}
	\end{split}
\end{equation}
with $i$ being the \textit{relative degree} of the system. Using Equation (\ref{eq:dy_i}) to formulate the control law leads to the following expression for the control input $\bm{u}$
\begin{equation}
	\begin{split}
		\bm{u} = L_{\bm{G}} L_{\bm{f}}^{i-1} \bm{h}(\bm{x})^{-1} (\bm{\nu} - L_{\bm{f}}^i\bm{h}(\bm{x})) 
		\label{eq:u_control_law_i}
	\end{split}
\end{equation}
Thus, Equation (\ref{eq:u_control_law_i}) applied to Equation (\ref{eq:dy_i}) yields the simple linear relation
\begin{equation}
	\begin{split}
		\bm{y}^i = \bm{\nu}
		\label{eq:lin_relation}
	\end{split}
\end{equation}
The \acrshort{NDI} method was widely adopted for civil and military aircrafts and has numerous of extensions \cite{Horn}. Nevertheless, it has some drawbacks. The major one is that the control law derived using the \acrshort{NDI} approach is dependent on the full system dynamics model \cite{Sieberling}. The equations of motion of an aircraft usually have a complicated nonlinear character. Thus, describing complex physical phenomena often leads to the inconsistency between the real aircraft and its mathematical representation used in the model. As some of those inconsistencies are inevitable there is a need to build a control law which performance is less dependent on the uncertainties of the model. A method called \acrfull{INDI} can be used to achieve this, it is discussed in the next subsection.

@@

Assuming that the output variable corresponds to the state varible ($y=x$), the incremental form of the system can be obtained by taking a Taylor series expansion of the Equation \ref{eq:nonlin_sys1}
\begin{equation}
	\begin{split}
		\bm{\dot{x}} &= \bm{f}(\bm{x}_0) + \bm{G}(\bm{x}_0)\bm{u}_0 \\
		&+ \frac{\partial}{\partial \bm{x}} [\bm{f}(\bm{x}) + \bm{G}(\bm{x})\bm{u}] \bigg|_{\bm{x}=\bm{x}_0,\bm{u}=\bm{u}_0} (\bm{x}-\bm{x}_0) \\
		&+ \frac{\partial}{\partial \bm{u}} [\bm{f}(\bm{x}) + \bm{G}(\bm{x})\bm{u}] \bigg|_{\bm{x}=\bm{x}_0,\bm{u}=\bm{u}_0} (\bm{u}-\bm{u}_0) 
		\label{eq:nonlin_sys_taylor}
	\end{split}
\end{equation}
The first term on the right side of the Equation \ref{eq:nonlin_sys_taylor} is $\bm{\dot{x}_0}$. Also, evaluating the differentiation of the third term leads to 
\begin{equation}
	\begin{split}
		\bm{\dot{x}} &= \bm{\dot{x}}_0 \\ 
		&+ \frac{\partial}{\partial \bm{x}} [\bm{f}(\bm{x}) + \bm{G}(\bm{x})\bm{u}] \bigg|_{\bm{x}=\bm{x}_0,\bm{u}=\bm{u}_0} (\bm{x}-\bm{x}_0) \\
		&+ \bm{G}(\bm{x}_0) (\bm{u}-\bm{u}_0) 
		\label{eq:nonlin_sys_taylor2}
	\end{split}
\end{equation}
The second term of the Equation \ref{eq:nonlin_sys_taylor2} contains partial derivative with respect to the state vector. Considering very small time increments of the controller loop and applying the \textit{principle of time scale separation} the second term vanishes. This is a valid assumption if the dynamics of the actuators are fast compared with the dynamics of the system \cite{Silva}. Thus, Equation \ref{eq:nonlin_sys_taylor2} is further simplified to 
\begin{equation}
	\begin{split}
		\bm{\dot{x}} = \bm{\dot{x}}_0 + \bm{G}(\bm{x}_0) (\bm{u}-\bm{u}_0) 
		\label{eq:nonlin_sys_indi}
	\end{split}
\end{equation}
By solving Equation \ref{eq:nonlin_sys_indi} for $\bm{u}$ and substituting $\bm{\dot{y}}$ with $\bm{\nu}$, the \acrshort{INDI} control law is obtained
\begin{equation}
	\begin{split}
		\bm{u} = \bm{u}_0 + \bm{G}(\bm{x}_0)^{-1} (\bm{\nu} - \bm{\dot{x}}_0)
		\label{eq:u_control_law_indi}
	\end{split}
\end{equation}
where $\bm{\dot{x}}_0$ is a measurable value from the previous step, $\bm{u_0}$ the control input from the previous step, $\bm{\nu}$ the reference value and $\bm{G}(\bm{x}_0)$ the control effectiveness matrix. With $\bm{\Delta u}=\bm{u}-\bm{u}_0$ the control law from Equation \ref{eq:u_control_law_indi} represents an incremental version of Equation \ref{eq:u_control_law}. Instead of computing the complete control input command $\bm{u}$, this control law results in computing the increment of the control input $\bm{\Delta u}$ and adding it to the previous value $\bm{u}_0$. As it is less dependent on the model of the system dynamics, it is able to increase the robustness of the system \cite{Sieberling}.

@@

The Crazyflie's main application \acrfull{MCU} is STM32F405. It runs the firmware with frequency of $1000~\si{\Hz}$ and communicates with a large number of peripheral devices such as Bluetooth and long range radio, power management system \acrshort{MCU}, \acrfull{IMU} etc.. The \acrfull{IMU} consists of the 3-axis accelerometer, the 3-axis gyroscope and the high precision pressure sensor.

@@

The core of the Crazyflie simulation is the model of the quadrotor dynamics. It is based on dynamic equations of motion presented in Chapter \ref{sec:eqs_motion}. Similarly to section \ref{subsec: indi_outer}, it was assumed that the sum of the forces in the linear momentum equation is composed of three components, namely gravitational, propulsive and aerodynamic. The expressions of the gravity and propulsive forces have not been changed, so the Equations \ref{eq:Fg} and \ref{eq:Fp} were adopted for the simulation model. The thrust value $T$ was modelled as a linear function of rotational rates of the propellers 
\begin{equation}
	\begin{split}
		T = - k_F (\Omega_1 + \Omega_2 + \Omega_3 + \Omega_4)
		\label{eq:thrust}
	\end{split}
\end{equation}
where $k_F$ is the force constant of the rotors. In subsection \ref{subsec:thrust_mapping} it is shown how to estimate the thrust coefficient directly from the flight data. However, for the simulation model $k_F$ was approximated based on the assumption that the influence of the force constant of the rotors $k_F$ (considering the lever arm) on the total moment is greater than the one of the moment constant of the rotors $k_M$, and that the \textit{thrust to weight ratio} expression is $\frac{T}{W} \approx 2$ (as the real Crazyflie quadrotor is able to hover at half throttle).

@@

The inner loop \acrshort{INDI} controller relies on the measurement of the rotor angular rates. If the actuator feedback is not available, it is possible to use its model instead. The model of the actuator dynamics was assumed to be a first order lag filter with the following transfer function defined in a continuous Laplace domain
\begin{equation}
	\begin{split}
		A(s) = \frac{k}{1+Ts}
		\label{eq:act_dynamics_c}
	\end{split}
\end{equation}
where $k$ is the gain and $T$ the time constant. Section \ref{sec:implementation_on_hardware} shortly describes the process of using flight data to estimate the time constant $T$. In the Simulink model it was assumed that the actuator feedback is available, hovewer for the implementation on hardware it is necessary to have a discrete version of the transfer function in Equation \ref{eq:act_dynamics_c}. Transforming it from continuous domain into discrete by applying \textit{Zero-Order Hold method} results in
\begin{equation}
	\begin{split}
		A(z) = \frac{k\alpha}{z+(\alpha-1)}
		\label{eq:act_dynamics_d}
	\end{split}
\end{equation}
with $\alpha = 1-e^{\frac{-T_S}{T}}$ and sample time $T_S$. The default frequency with which the Crazyflie controller updates its state is $500~\si{\Hz}$. Thus, sampling time $T_S$ was set to the reciprocal value of the default frequency.

@@

To obtain $T_c$, current thrust value $T_0$ is filtered with a second order filter $F(z)$ ($\omega_n=8~\si{\radian/\second}$, $\zeta=0.707$) and passed through the model of the actuator dynamics $A'(z)$. The result is then added to the thrust increment $\tilde{T}$, provided by the outer loop \acrshort{INDI}. This computation is graphically shown in Figure \ref{fig:outer_loop_hw}. The part of the outer loop which is different from the one used in the Simulink model (see Figure \ref{fig:indi_outer_croped}) is presented in blue color.

@@

\chapter*{Appendix} \label{sec:appendix}
% Add Appendix chapter manually to the Table of Contents because Latex doesn't automatically include nonnumerated (...*) chapters/sections to the TOC
\addcontentsline{toc}{chapter}{Appendix}

>>>>

%% Add List of Tables
%\renewcommand{\cfttabfont}{Table }				% Add "Figure" to the LOF
%\renewcommand\cfttabaftersnum{:} 				% Put ":" after the figure num 
%\setlength{\cfttabindent}{0pt}					% Remove left indent
%\setlength\cftbeforetabskip{-0.2cm}				% Space between tables
%\addtocontents{lot}{\vspace*{10pt}}			    % Set distance between LOT %title and list
%\listoftables{}

%% Manually add Chapter names to the header (per default not included by Latex)
%\thispagestyle{fancy_beginning}
%\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
%\chaptermark{List of Tables}

%%Insert empty page after the list of tables 
%\newpage\null\thispagestyle{empty}\newpage

@@

% Add Table of Symbols
%\chapter*{Table of Symbols} \label{sec:symbols}
\mbox{}
\nomwithdim{B, 001}{\( A(s),~A(z) \)}{Transfer function of the actuator dynamics}{}{--}
\nomwithdim{B, 002}{\( A'(s),~A'(z) \)}{Transfer function of the actuator dynamics model}{}{--}
\nomwithdim{B, 002}{\( a(t) \)}{Function of the first order lag element in time domain}{}{--}
\nomwithdim{B, 005}{\( b \)}{Lever arm of the rotors to the C.G. along the body $y$-axis}{}{$m$}
\nomwithdim{B, 010}{\( d \)}{Disturbance}{}{$m/s^2$}
\nomwithdim{B, 010}{\( d_0, d_1, d_2 \)}{Denominator coefficients of the discrete second order filter}{}{--}
\nomwithdim{B, 015}{\( E(t) \)}{Objective function}{}{$m$}
\nomwithdim{B, 020}{\( \bm{F} \)}{Force vector}{}{$N$}
\nomwithdim{B, 020}{\( \bm{F}_A \)}{Aerodynamic force vector}{}{$N$}
\nomwithdim{B, 020}{\( \bm{F}_G \)}{Gravitational force vector}{}{$N$}
\nomwithdim{B, 020}{\( \bm{F}_P \)}{Propulsive force vector}{}{$N$}
\nomwithdim{B, 021}{\( \bm{f}(\bm{x}) \)}{Nonlinear vector field}{}{--}
\nomwithdim{B, 025}{\( \bm{G} \)}{Control effectiveness matrix of the outer loop}{}{--}
\nomwithdim{B, 025}{\( \bm{G}_1 \)}{Control effectiveness matrix of the inner loop}{}{--}
\nomwithdim{B, 025}{\( \bm{G}_2 \)}{Control effectiveness matrix of the inner loop}{}{--}
\nomwithdim{B, 025}{\( \bm{G}_{inner} \)}{Dynamics matrix of the inner loop}{}{--}
\nomwithdim{B, 025}{\( \bm{G}_{outer} \)}{Dynamics matrix of the outer loop}{}{--}
\nomwithdim{B, 025}{\( \bm{G}(x) \)}{Input matrix}{}{--}
\nomwithdim{B, 025}{\( g \)}{Gravitational acceleration}{}{$m/s^2$}
\nomwithdim{B, 030}{\( H(s),~H(z) \)}{Transfer function of the second order filter}{}{--}
\nomwithdim{B, 031}{\( \bm{h}(\bm{x}) \)}{Nonlinear vector field}{}{--}
\nomwithdim{B, 035}{\( \bm{I} \)}{Inertia tensor of the quadrotor}{}{$Nm^2$}
\nomwithdim{B, 036}{\( \bm{I_{rzz}} \)}{$zz$-element of the inertia tensor of the rotor}{}{$Nm^2$}
\nomwithdim{B, 036}{\( i \)}{Relative degree of the dynamic system}{}{--}
\nomwithdim{B, 040}{\( K \)}{Compensation gain}{}{--}
\nomwithdim{B, 040}{\( K_{cmd} \)}{Thrust mapping parameter}{}{--}
\nomwithdim{B, 041}{\( k \)}{Drag coefficient}{}{$kg/s$}
\nomwithdim{B, 041}{\( k \)}{Gain of the actuator dynamics}{}{--}
\nomwithdim{B, 041}{\( k_F \)}{Force constant of the rotors}{}{$\frac{N}{rad/s}$}
\nomwithdim{B, 041}{\( k_M \)}{Moment constant of the rotors}{}{$\frac{Nm}{rad/s}$}
\nomwithdim{B, 045}{\( L \)}{Lie derivative operator}{}{--}
\nomwithdim{B, 045}{\( l \)}{Lever arm of the rotors to the C.G. along the body $y$-axis}{}{$m$}
\nomwithdim{B, 050}{\( \bm{M} \)}{Moment vector}{}{$Nm$}
\nomwithdim{B, 050}{\( \bm{M}_A \)}{Aerodynamic moment vector}{}{$Nm$}
\nomwithdim{B, 050}{\( \bm{M}_c \)}{Control moment vector}{}{$Nm$}
\nomwithdim{B, 050}{\( \bm{M}_G \)}{Gravitational moment vector}{}{$Nm$}
\nomwithdim{B, 050}{\( \bm{M}_{gyro} \)}{Moment vector due to the gyroscopic effects of the rotor}{}{$Nm$}
\nomwithdim{B, 050}{\( \bm{M}_{OB} \)}{Transformation matrix from the body-fixed into NED frame}{}{--}
\nomwithdim{B, 050}{\( \bm{M}_P \)}{Propulsion moment vector}{}{$Nm$}
\nomwithdim{B, 052}{\( m \)}{Mass of the quadrotor}{}{$kg$}
\nomwithdim{B, 052}{\( m_{cf} \)}{Mass of the Crazyflie quadrotor}{}{$kg$}
\nomwithdim{B, 053}{\( m_r \)}{Additional mass (disturbance)}{}{$kg$}
\nomwithdim{B, 055}{\( n \)}{Number of samples}{}{$m$}
\nomwithdim{B, 055}{\( n_0, n_1, n_2 \)}{Numerator coefficients of the discrete second order filter}{}{--}
\nomwithdim{B, 060}{\( P \)}{Parameter}{}{--}
\nomwithdim{B, 060}{\( p \)}{Roll rate}{}{$rad/s$}
\nomwithdim{B, 065}{\( q \)}{Pitch rate}{}{$rad/s$}
\nomwithdim{B, 070}{\( r \)}{Yaw rate}{}{$rad/s$}
\nomwithdim{B, 075}{\( s \)}{Laplace variable}{}{--}
\nomwithdim{B, 080}{\( T \)}{Thrust}{}{$N$}
\nomwithdim{B, 080}{\( T \)}{Time constant of the actuator dynamics}{}{$s$}
\nomwithdim{B, 080}{\( T_{cmd} \)}{Thrust in motor units}{}{--}
\nomwithdim{B, 080}{\( T_s \)}{Sample time of the controller}{}{$s$}
\nomwithdim{B, 081}{\( \tilde{T} \)}{Thrust increment}{}{$N$}
\nomwithdim{B, 081}{\( t \)}{Time}{}{$s$}
\nomwithdim{B, 085}{\( \bm{u} \)}{Input vector}{}{--}
\nomwithdim{B, 085}{\( \bm{u}_c \)}{Control vector}{}{--}
\nomwithdim{B, 085}{\( u \)}{$x$-component of the velocity vector}{}{$m/s$}
\nomwithdim{B, 090}{\( V \)}{Component of the velocity vector}{}{$m/s$}
\nomwithdim{B, 091}{\( v \)}{$y$-component of the velocity vector}{}{$m/s$}
\nomwithdim{B, 091}{\( \bm{v} \)}{Velocity vector}{}{$m/s$}
\nomwithdim{B, 095}{\( W \)}{Weight of the quadrotor}{}{$N$}
\nomwithdim{B, 095}{\( w \)}{$z$-component of the velocity vector}{}{$m/s$}
\nomwithdim{B, 100}{\( \bm{x} \)}{State vector}{}{--}
\nomwithdim{B, 100}{\( x \)}{Position coordinate in $x$-direction}{}{$m$}
\nomwithdim{B, 105}{\( \bm{y} \)}{Output vector}{}{--}
\nomwithdim{B, 105}{\( y \)}{Position coordinate in $y$-direction}{}{$m$}
\nomwithdim{B, 110}{\( \bm{z} \)}{Transformed state vector}{}{--}
\nomwithdim{B, 110}{\( z \)}{z-Transformation variable}{}{--}
\nomwithdim{B, 110}{\( z \)}{Position coordinate in $z$-direction}{}{$m$}

\nomwithdim{G, 200}{\( \alpha \)}{Parameter of the discrete first order lag element}{}{$N$}
\nomwithdim{G, 205}{\( \zeta \)}{Relative damping coefficient of the second order filter}{}{--}
\nomwithdim{G, 206}{\( \bm{\eta} \)}{Attitude vector}{}{$rad$}
\nomwithdim{G, 210}{\( \Theta \)}{Pitch angle}{}{$rad$}
\nomwithdim{G, 210}{\( \tilde{\Theta} \)}{Pitch angle increment}{}{$rad$}
\nomwithdim{G, 210}{\( \Theta_c \)}{Control pitch angle}{}{$rad$}
\nomwithdim{G, 215}{\( \bm{\nu} \)}{Virtual control input vector}{}{--}
\nomwithdim{G, 215}{\( \bm{\nu}_{\bm{\dot{v}}} \)}{Virtual control input vector of the outer loop}{}{$m/s^2$}
\nomwithdim{G, 215}{\( \bm{\nu}_{\bm{\dot{\omega}}} \)}{Virtual control input vector of the inner loop}{}{$rad/s^2$}
\nomwithdim{G, 219}{\( \bm{\xi} \)}{Position vector}{}{$m$}
\nomwithdim{G, 220}{\( \Phi \)}{Roll/Bank angle}{}{$rad$}
\nomwithdim{G, 220}{\( \tilde{\Phi} \)}{Roll angle increment}{}{$rad$}
\nomwithdim{G, 220}{\( \Phi_c \)}{Control roll angle}{}{$rad$}
\nomwithdim{G, 221}{\( \bm{\phi}(\bm{x}) \)}{State transformation function}{}{--}
\nomwithdim{G, 225}{\( \bm{\chi} \)}{Wind vector}{}{$m/s$}
\nomwithdim{G, 230}{\( \Psi \)}{Yaw/Bank angle}{}{$rad$}
\nomwithdim{G, 235}{\( \bm{\Omega} \)}{Propeller rate vector of the four rotors}{}{$rad/s$}
\nomwithdim{G, 235}{\( \bm{\Omega}_i \)}{Propeller rate of the i-th rotor}{}{$rad/s$}
\nomwithdim{G, 235}{\( \tilde{\bm{\Omega}} \)}{Propeller rate increment}{}{$rad/s$}
\nomwithdim{G, 235}{\( \bm{\Omega}_c \)}{Propeller rate control vector of the four rotors around}{}{$rad/s$}
\nomwithdim{G, 236}{\( \bm{\omega} \)}{Angular velocity vector of the quadrotor}{}{$rad/s$}
\nomwithdim{G, 236}{\( \omega_n \)}{Cutoff frequency of the second order filter}{}{$rad/s$}

\nomwithdim{S}{\( 0 \)}{Initial point in time}{}{--}
\nomwithdim{S}{\( a \)}{Passed through the actuator dynamics}{}{--}
\nomwithdim{S}{\( B \)}{Body-fixed coordinate frame}{}{--}
\nomwithdim{S}{\( D \)}{Down}{}{--}
\nomwithdim{S}{\( E \)}{East}{}{--}
\nomwithdim{S}{\( f \)}{Filtered}{}{--}
\nomwithdim{S}{\( G \)}{Center of gravity}{}{--}
\nomwithdim{S}{\( G \)}{Gravitational}{}{--}
\nomwithdim{S}{\( K \)}{Kinematic coordinate frame}{}{--}
\nomwithdim{S}{\( N \)}{North}{}{--}
\nomwithdim{S}{\( O \)}{North-East-Down coordinate frame}{}{--}
\nomwithdim{S}{\( R \)}{Reference point}{}{--}
\nomwithdim{S}{\( x \)}{$x$-component of a variable}{}{--}
\nomwithdim{S}{\( y \)}{$y$-component of a variable}{}{--}
\nomwithdim{S}{\( z \)}{$z$-component of a variable}{}{--}

\nomwithdim{X, 400}{\( L \)}{Lie derivative operator}{}{--}
\nomwithdim{X, 401}{\( \nabla \)}{Nabla-Operator}{}{--}

\renewcommand{\nomname}{Table of Symbols}

\printnomenclature[6em]

% Manually add Chapter names to the header (per default not included by Latex) 
\pagestyle{fancy_beginning}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\chaptermark{Table of Symbols}

@@

In this subsection, the \acrlong{NDI} method is explained. The \acrshort{NDI} approach is based on feedback linearization and is also called \textit{Input-Output Linearization}. Often, such type of controllers is involved in tracking control tasks, where the objective is to track some desired trajectory \cite{Slotine}. To derive it, consider the following nonlinear system
\begin{subequations}
	\begin{align}
		&\bm{\dot{x}} = \bm{f}(\bm{x}) + \bm{G}(\bm{x})\bm{u} \label{eq:nonlin_sys1} \\
		&\bm{y} = \bm{h}(\bm{x}) \label{eq:nonlin_sys2}
	\end{align}
	\label{eq:nonlin_sys}
\end{subequations}
\hspace{-5pt}where $\bm{x} \in \mathbb{R}^{n \times 1}$ is the state vector, $\bm{u} \in \mathbb{R}^{m \times 1}$ the input vector, $\bm{y} \in \mathbb{R}^{m \times 1}$ the output vector, $\bm{f}(\bm{x}) \in \mathbb{R}^{n \times 1}$ and $\bm{h}(\bm{x}) \in \mathbb{R}^{m \times 1}$ nonlinear vector fields and $\bm{G} \in \mathbb{R}^{m \times n}$ an input matrix. Note that the system presented in Equations (\ref{eq:nonlin_sys}) is affine in the input, which is not allways fulfilled. Using a state transformation $\bm{z} = \bm{\phi}(\bm{x})$, the affine system from Equation \ref{eq:nonlin_sys1} can be transformed into a \textit{normal} (\textit{canonical}) representation.

@@

In the example provided above the input-output relationsip was found after the first differentiation of the output $\bm{y}$. But if after the first differentiation the term $L_{\bm{G}}\bm{h}(\bm{x})$ is zero, output $\bm{y}$ has to be differentiated until the Lie derivative with respect to $\bm{G}$ is nonzero. The $i$-th derivative of the output is then
\begin{equation}
	\begin{split}
		\frac{\partial^i\bm{y}}{\partial t} = \frac{\partial^i\bm{h}(\bm{x})}{\partial t} = L_{\bm{f}}^i \bm{h}(\bm{x}) + L_{\bm{G}} L_{\bm{f}}^{i-1} \bm{h}(\bm{x}) \bm{u}
		\label{eq:dy_i}
	\end{split}
\end{equation}
with $i$ being the \textit{relative degree} of the system. Using Equation (\ref{eq:dy_i}) to formulate the control law leads to the following expression for the control input $\bm{u}$
\begin{equation}
	\begin{split}
		\bm{u} = L_{\bm{G}} L_{\bm{f}}^{i-1} \bm{h}(\bm{x})^{-1} (\bm{\nu} - L_{\bm{f}}^i\bm{h}(\bm{x})) 
		\label{eq:u_control_law_i}
	\end{split}
\end{equation}
Thus, Equation (\ref{eq:u_control_law_i}) applied to Equation (\ref{eq:dy_i}) yields the simple linear relation
\begin{equation}
	\begin{split}
		\bm{y}^i = \bm{\nu}
		\label{eq:lin_relation}
	\end{split}
\end{equation}
The \acrshort{NDI} method was widely adopted for civil and military aircrafts and has numerous of extensions \cite{Horn}. Nevertheless, it has some drawbacks. The major one is that the control law derived using the \acrshort{NDI} approach is dependent on the full system dynamics model \cite{Sieberling}. The equations of motion of an aircraft usually have a complicated nonlinear character. Thus, describing complex physical phenomena often leads to the inconsistency between the real aircraft and its mathematical representation used in the model. As some of those inconsistencies are inevitable there is a need to build a control law which performance is less dependent on the uncertainties of the model. A method called \acrlong{INDI} can be used to achieve this, it is discussed in the next subsection.

@@

Assuming that the output variable corresponds to the state varible ($\bm{y}=\bm{x}$), the incremental form of the system can be obtained by taking a Taylor series expansion of the Equation \ref{eq:nonlin_sys1}
\begin{equation}
	\begin{split}
		\bm{\dot{x}} &= \bm{f}(\bm{x}_0) + \bm{G}(\bm{x}_0)\bm{u}_0 \\
		&+ \frac{\partial}{\partial \bm{x}} [\bm{f}(\bm{x}) + \bm{G}(\bm{x})\bm{u}] \bigg|_{\bm{x}=\bm{x}_0,\bm{u}=\bm{u}_0} (\bm{x}-\bm{x}_0) \\
		&+ \frac{\partial}{\partial \bm{u}} [\bm{f}(\bm{x}) + \bm{G}(\bm{x})\bm{u}] \bigg|_{\bm{x}=\bm{x}_0,\bm{u}=\bm{u}_0} (\bm{u}-\bm{u}_0) 
		\label{eq:nonlin_sys_taylor}
	\end{split}
\end{equation}
The first term on the right side of the Equation \ref{eq:nonlin_sys_taylor} is $\bm{\dot{x}_0}$. Also, evaluating the differentiation of the third term leads to 
\begin{equation}
	\begin{split}
		\bm{\dot{x}} &= \bm{\dot{x}}_0 \\ 
		&+ \frac{\partial}{\partial \bm{x}} [\bm{f}(\bm{x}) + \bm{G}(\bm{x})\bm{u}] \bigg|_{\bm{x}=\bm{x}_0,\bm{u}=\bm{u}_0} (\bm{x}-\bm{x}_0) \\
		&+ \bm{G}(\bm{x}_0) (\bm{u}-\bm{u}_0) 
		\label{eq:nonlin_sys_taylor2}
	\end{split}
\end{equation}
The second term of the Equation \ref{eq:nonlin_sys_taylor2} contains partial derivative with respect to the state vector. Considering very small time increments of the controller loop and applying the \textit{principle of time scale separation} the second term vanishes. This is a valid assumption if the dynamics of the actuators are fast compared with the dynamics of the system \cite{Silva}. Thus, Equation \ref{eq:nonlin_sys_taylor2} is further simplified to 
\begin{equation}
	\begin{split}
		\bm{\dot{x}} = \bm{\dot{x}}_0 + \bm{G}(\bm{x}_0) (\bm{u}-\bm{u}_0) 
		\label{eq:nonlin_sys_indi}
	\end{split}
\end{equation}
By solving Equation \ref{eq:nonlin_sys_indi} for $\bm{u}$ and substituting $\bm{\dot{y}}$ with $\bm{\nu}$, the \acrshort{INDI} control law is obtained
\begin{equation}
	\begin{split}
		\bm{u} = \bm{u}_0 + \bm{G}(\bm{x}_0)^{-1} (\bm{\nu} - \bm{\dot{x}}_0)
		\label{eq:u_control_law_indi}
	\end{split}
\end{equation}
where $\bm{\dot{x}}_0$ is a measurable value from the previous step, $\bm{u_0}$ the control input from the previous step, $\bm{\nu}$ the reference value and $\bm{G}(\bm{x}_0)$ the control effectiveness matrix. With $\bm{\Delta u}=\bm{u}-\bm{u}_0$ the control law from Equation \ref{eq:u_control_law_indi} represents an incremental version of Equation \ref{eq:u_control_law}. Instead of computing the complete control input command $\bm{u}$, this control law results in computing the increment of the control input $\bm{\Delta u}$ and adding it to the previous value $\bm{u}_0$. As it is less dependent on the model of the system dynamics, it is able to increase the robustness of the system \cite{Sieberling}.

@@

The Crazyflie's main application \acrfull{MCU} is STM32F405. It runs the firmware with frequency of $1000~\si{\Hz}$ and communicates with a large number of peripheral devices such as Bluetooth and long range radio, power management system \acrshort{MCU}, \acrfull{IMU} etc.. The \acrlong{IMU} consists of the 3-axis accelerometer, the 3-axis gyroscope and the high precision pressure sensor.

@@

The core of the Crazyflie simulation is the model of the quadrotor dynamics. It is based on dynamic equations of motion presented in Chapter \ref{sec:eqs_motion}. Similarly to section \ref{subsec: indi_outer}, it was assumed that the sum of the forces in the linear momentum equation is composed of three components, namely gravitational, propulsive and aerodynamic. The expressions of the gravity and propulsive forces have not been changed, so the Equations \ref{eq:Fg} and \ref{eq:Fp} were adopted for the simulation model. To achieve a simple relationship between the thrust of a quadrotor and the propeller rates, thrust value $T$ was modelled as a linear function of propeller rates $\bm{\Omega}$ 
\begin{equation}
	\begin{split}
		T = - k_F (\Omega_1 + \Omega_2 + \Omega_3 + \Omega_4)
		\label{eq:thrust}
	\end{split}
\end{equation}
where $k_F$ is the force constant of the rotors. In subsection \ref{subsec:thrust_mapping} it is shown how to estimate the thrust coefficient directly from the flight data. However, for the simulation model $k_F$ was approximated based on the assumption that the influence of the force constant of the rotors $k_F$ (considering the lever arm) on the total moment is greater than the one of the moment constant of the rotors $k_M$, and that the \textit{thrust to weight ratio} expression is $\frac{T}{W} \approx 2$ (as the real Crazyflie quadrotor is able to hover at half throttle).

@@

The inner loop \acrshort{INDI} controller relies on the measurement of the rotor angular rates. If the actuator feedback is not available, it is possible to use its model instead. The model of the actuator dynamics was assumed to be a first order lag filter with the following transfer function defined in a continuous Laplace domain
\begin{equation}
	\begin{split}
		A(s) = \frac{k}{1+Ts}
		\label{eq:act_dynamics_c}
	\end{split}
\end{equation}
where $k$ is the gain and $T$ the time constant. Section \ref{sec:implementation_on_hardware} shortly describes the process of using flight data to estimate the time constant $T$. In the Simulink model it was assumed that the actuator feedback is available, hovewer for the implementation on hardware it is necessary to have a discrete version of the transfer function in Equation \ref{eq:act_dynamics_c}. Transforming it from continuous domain into discrete by applying \textit{Zero-Order Hold method} results in
\begin{equation}
	\begin{split}
		A(z) = \frac{k\alpha}{z+(\alpha-1)}
		\label{eq:act_dynamics_d}
	\end{split}
\end{equation}
with $\alpha = 1-e^{\frac{-T_s}{T}}$ and sample time $T_s$. The default frequency with which the Crazyflie controller updates its state is $500~\si{\Hz}$. Thus, sampling time $T_s$ was set to the reciprocal value of the default frequency.

@@

To obtain $T_c$, current thrust value $T_0$ is filtered with a second order filter $H(z)$ ($\omega_n=8~\si{\radian/\second}$, $\zeta=0.707$) and passed through the model of the actuator dynamics $A'(z)$. The result is then added to the thrust increment $\tilde{T}$, provided by the outer loop \acrshort{INDI}. This computation is graphically shown in Figure \ref{fig:outer_loop_hw}. The part of the outer loop which is different from the one used in the Simulink model (see Figure \ref{fig:indi_outer_croped}) is presented in blue color.

@@

%\chapter*{Appendix} \label{sec:appendix}
%% Add Appendix chapter manually to the Table of Contents because Latex doesn't automatically include nonnumerated (...*) chapters/sections to the TOC
%\addcontentsline{toc}{chapter}{Appendix}
